---
title: "Assignment 2"
author: "Ya-Chen Lin"
date: "2015 09 12"
output: pdf_document
---
#Question 01:   
\textit{Working with data in the datasets folder on the course GitHub repo, you will find a file called cancer.csv, a dataset in comma-separated values (csv) format. This is a large cancer incidence dataset that summarizes the incidence of different cancers for various subgroups.}  
```{r}
#i:Load the data set into R and make it a data frame called cancer.df 
cancer.df <- data.frame(read.csv('cancer.csv', fill=TRUE, header = TRUE))
#ii:Determine the number of rows and columns in the data frame
nrow(cancer.df)
ncol(cancer.df)
#iii:Extract the names of the columns in cancer.df
colnames(cancer.df)
#iv:Report the value of the 3000th row in column 6
cancer.df[3000,6]
#v:Report the contents of the 172nd row.
cancer.df[172,]
#vi:Create a new column that is the incidence rate (per 100,000) for each row.
cancer.df$incidence_rate <- ( cancer.df$incidence )/100000
colnames(cancer.df)
#vii:How many subgroups (rows) have a zero incidence rate?
sum(cancer.df$incidence_rate == 0)
#viii:Find the subgroup with the highest incidence rate
cancer.df[which.max(cancer.df$incidence_rate),]
```
#Question 02:  
\textit{i.Create the following vector: x <- c("5","12","7"). Which of the following commands will produce an error message? For each command, Either explain why they should be errors, or explain the non-erroneous result. }
```{r}

x <- c("5","12","7")
class(x)
```
x consists of three "character" arguments
```{r}
max(x)
```
Within maxima command, it can return numeric or character arguments. Thus we can get value "7" as character.
```{r}
sort(x)
```
Sort can return objects with a numeric, complex, character or logical vectors. Thus we can get the order of x.
```{r}
#sum(x) will give an error which couldn't be shown in PDF.
```
Sum can only return numeric or complex or logical vectors. Thus in this case where x consists only character value, we will receive an error message.  
<br><br>
\textit{ii:For the next two commands, either explain their results, or why they should produce errors. }
```{r}
y <- c("5",7,12)
#y[2] + y[3] will give an error message which couldn't be shown in PDF
```
y is cassified as character variable. + is only used in numerics not character. Thus by adding them together, we will recive the error message:"non-numeric" argument.   
<br><br>
\textit{iii:For the next two commands, either explain their results, or why they should produce errors.}
```{r}
z <- data.frame(z1="5",z2=7,z3=12)
z[1,2] + z[1,3]
class(z[1,2])
class(z[1,3])
```
When characteric arguments are passed to data frame, they are numeric arguments, as in the class commands. Thus, we can use + operator to add two numeric values together.  
```{r}
```

#Question 03:  
\textit{Data Structure: Give R expressions that return the following matrices and vectors (i.e. do not construct them manually).}
```{r}
#i.
c(x <- 1:8, rev(x[-length(x)]))
```
```{r}
#ii
rep(1:5, c(1:5))
```
```{r}
#iii
1-diag(3)
```
```{r}
#iv:
matrix(c(1^(1:5), 2^(1:5), 3^(1:5), 4^(1:5)), nrow =5, ncol=4)
```

#Question 04:
\textit{i:Let $h(x,n)=1+x+x^2+\ldots+x^n = \sum_{i=0}^n x^i$. Write an R program to calculate $h(x,n)$ using a for loop.}
```{r}
#pick any X and n
x=5
n=10
A<- NULL
B <- rep(x,(n+1))
for(i in 0:n){
A[(i+1)] <-  B[(i+1)]^i
}
sum(A)
```

\textit{iia:Find the sum of all the multiples of 3 or 5 below 1,000.}
```{r}
x <- c(1:999)
sum(which(x%%3 == 0 | x%%5 == 0))
```

\textit{iib:Find the sum of all the multiples of 4 or 7 below 1,000,000}
```{r}
x <- c(1:999999)
sum(as.numeric(which(x%%4 == 0 | x%%7 == 0)))
```

\textit{iii:Each new term in the Fibonacci sequence is generated by adding the previous two terms. By starting with 1 and 2, the first 10 terms will be $(1, 2, 3, 5, 8, 13, 21, 34, 55, 89)$. Write an R program to calculate the sum of the first 15 even-valued terms.}

```{r}
B <- c(1,2,rep(0,50))
for (i in 3:52){
B[i] <- B[i-1] + B[i-2]
}
evenB <- B[which(B %% 2 == 0)]
sum(evenB[1:15])
```








