---
title: "Assignment 3"
author: "Ya-Chen Lin"
date: "2015 M09 23"
output: pdf_document
---

#Question 02:
\textit{Write a simulation to calculate the power for the following study design.}

Find the power when the sample size is 100 patients. 
```{r}
set.seed(1)
#Create a function with n=100 and return the pvalue
p<- function(){
treatment <- matrix(rbinom(n=100, size=1, prob=1/2))
outcome <- matrix(rnorm(100, mean=60, sd=20))
study <- cbind(treatment, outcome)
colnames(study) <- c('treatment' ,'outcome')
study <- data.frame(study)
for(i in 1:100){
  if(study[i,1] == 1){
    study[i,2] <- study[i,2] + 5
  }
}
mod.study <- lm(outcome ~ treatment, data=study)
pvalue <- summary(mod.study)$coefficients['treatment',4]
return(pvalue)
}
#Simulate this function for 1000 times
loops <- 1000
pb <- c()
ps <- 0
for(i in seq(loops)){
  pb[i] <- p()  
}
power100 <- sum(pb[] <= 0.05) *100 / loops
power100
```
Find the power when the sample size is 1000 patients. 
```{r}
set.seed(2)
#Create a function with n=1000 and return pvalue
p<- function(){
treatment <- matrix(rbinom(n=1000, size=1, prob=1/2))
outcome <- matrix(rnorm(1000, mean=60, sd=20))
study <- cbind(treatment, outcome)
colnames(study) <- c('treatment' ,'outcome')
study <- data.frame(study)
for(i in 1:1000){
  if(study[i,1] == 1){
    study[i,2] <- study[i,2] + 5
  }
}
mod.study <- lm(outcome ~ treatment, data=study)
pvalue <- summary(mod.study)$coefficients['treatment',4]
return(pvalue)
}
#Simulate this function for 1000 times
loops <- 1000
pb <- c()
ps <- 0
for(i in seq(loops)){
  pb[i] <- p()  
}
power1000 <- sum(pb[] <= 0.05) *100 / loops
power1000
```
#Question 03:
\textit{Obtain a copy of the football-values lecture.} 
```{r}
rb <- read.csv('https://raw.githubusercontent.com/couthcommander/football-values/master/2015/proj_rb15.csv')
rb <- rb[, 3:10]
```
1. Show the correlation matrix of this data set.
```{r}
cor(rb)
```
2. Generate a data set with 30 rows that has a similar correlation structure. Repeat the procedure 10,000 times and return the mean correlation matrix.
```{r}
set.seed(3)
rb <- read.csv('https://raw.githubusercontent.com/couthcommander/football-values/master/2015/proj_rb15.csv')
rb <- rb[, 3:10]
means.rb <- colMeans(rb)
vcov.rb <- var(rb)
library(MASS)
rb.sim.c <- 0
loops <- 10000
for ( i in seq(loops)){
rb.sim <- mvrnorm (30, mu=means.rb, Sigma = vcov.rb)
rb.sim <- data.frame(rb.sim)
rb.sim.c <- rb.sim.c + (cor(rb.sim) / loops)
}
rb.sim.c
```
3.Generate a data set with 30 rows that has the exact correlation structure as the original data set. 
```{r}
rbn <- mvrnorm(30, mu=means.rb, Sigma = vcov.rb, empirical = TRUE)
cor(rb)
cor(rbn)
```
With empirical = TRUE, we can get data with exact same correlation  

#Question 04:  
1.  
```{r}
#\begin{align}
#P(B) &=\sum_{j} P(B|A_j)P(A_j),\\ 
#& \Rightarrow P(A_i|B)\frac{P(B|A_i)P(A_i)}{\sum_{j}P(B|A_j)P(A_i)}
#\end{align}

```
\begin{align}
P(B) &=\sum_{j} P(B|A_j)P(A_j),\\ 
& \Rightarrow P(A_i|B)\frac{P(B|A_i)P(A_i)}{\sum _j P(B|A_j)P(A_i)}
\end{align}

2.  
```{r}
#$\hat{f}(\zeta)=\displaystyle\int_{-\infty}^{\infty} f(x) e^{-2{\pi}ix{\zeta}} dx$
```
$\hat{f}(\zeta)=\displaystyle\int_{-\infty}^{\infty} f(x) e^{-2{\pi}ix{\zeta}} dx$

3.
```{r}
#$\mathbf{J}=\frac{d\mathbf{f}}{d\mathbf{x}}=\left[\frac{\partial \mathbf{f}}{\partial x_1}\cdots\frac{\partial\mathbf{f}}{\partial x_n}\right]=\left[ \begin{array}{cc} \frac{\partial f_1}{\partial x_1} \cdots\frac{\partial f_1}{\partial x_n} \\ \vdots \ddots\vdots \\ \frac{\partial f_m}{\partial x_1}\cdots\frac{\partial f_m}{\partial x_n}\end{array}\right]$
```
$\mathbf{J}=\frac{d\mathbf{f}}{d\mathbf{x}}=\left[\frac{\partial \mathbf{f}}{\partial x_1}\cdots\frac{\partial\mathbf{f}}{\partial x_n}\right]=\left[ \begin{array}{cc} \frac{\partial f_1}{\partial x_1} \cdots\frac{\partial f_1}{\partial x_n} \\ \vdots \ddots\vdots \\ \frac{\partial f_m}{\partial x_1}\cdots\frac{\partial f_m}{\partial x_n}\end{array}\right]$

### Notes/Grade:

50/50 points